\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-13 podc16/paper2.tex
integrated Binoy's comments

On top of enabling modular correctness proofs of algorithms like EPaxos, we expect that the modular structure of our generic leaderless algorithm will allow a principled theoretical and empirical evaluation of the trade-offs that can be achieved by different implementations of our two abstractions, as well as optimizations to their orchestration.
We have formalized our generic leaderless algorithm in TLA+ and have thoroughly model-checked our safety claims with the TLC model-checker\footnote{\url{http://losa.fr/leaderless}}.

>>>>

On top of enabling modular correctness proofs of algorithms like EPaxos, we expect that the modular structure of our generic leaderless algorithm will allow a principled theoretical and empirical evaluation of the trade-offs that can be achieved by different implementations of our two abstractions in varied environments such clusters or wide area networks, and on varied metrics such as agreement latency, impact of failures or conflicts, tolerance to slow processes, load
balancing, size of quorums, etc.
We have formalized\footnote{\url{http://losa.fr/leaderless}} and model-checked our generic leaderless algorithm with the TLA$^+$ toolbox.
